\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex

\begin{abstract}
Faceted Execution (FE) is a linguistic paradigm for dynamic
information flow control. Using faceted execution, secure program data
is represented by \emph{facets}: decision trees that encode how the
data should appear to its owner (represented by a label) versus everyone
else. When labels are allowed to be first-class (i.e., predicates that
decide at runtime which data to reveal), faceted execution enables
\emph{policy-agnostic programming}: a programming style that allows
privacy policies for data to be enforced independently of code that
computes on that data.

>>>>

\begin{abstract}
Faceted Execution is a linguistic paradigm for dynamic
information-flow control. Under faceted execution, secure program data
is represented by \emph{faceted} values: decision trees that encode how the
data should appear to its owner (represented by a label) versus everyone
else. When labels are allowed to be first-class (i.e., predicates that
decide at runtime which data to reveal), faceted execution enables
\emph{policy-agnostic programming}: a programming style that allows
privacy policies for data to be enforced independently of code that
computes on that data.
